\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities\\ Technical Report with Proves and Details

### 2018-07-04 fully-abstract-comp/technical-report.tex
Note on instruction set in tech report.

% At the moment of writing this, I am not sure why we thought about them, but it was related to hiding program lengths (and stack height).
% At this juncture, it does, however, not seem necessary to have opaque because sealed capabilities can do their job.

>>>>

% At the moment of writing this, I am not sure why we thought about them, but it was related to hiding program lengths (and stack height).
% At this juncture, it does, however, not seem necessary to have opaque because sealed capabilities can do their job.
\subsection{Notes on linear capabilities}
It seems reasonable to have enough instructions to let any program be able to make sufficient checks that it can verify that its execution won't fail.
With our current instruction set, a load may fail if a linear capability happens to be located at a memory address that on attempts to load from with a capability without write permission.
To make up for this, one could make an instruction that checks the linearity of a capability in memory without loading it.
It may not be practical to make such an instruction if linearity is kept track as a field on each capability, but it may be tractable if linearity tags are kept track of in a table.
